Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-02 body.tex
Table with the parameters of the shell

The gravitational potential,
gravitational attraction,
and
Marussi (gravity gradient) tensor
of a homogeneous spherical shell
are \citep{Grombein2013}

@@

>>>>

We must establish reference values to evaluate the error of the numerical
integration.

The homogeneous spherical shell is a convenient geometry with analytical
solutions for
the gravitational potential, attraction, and gravity gradient tensor \citep{Grombein2013}

@@

The computation point can be considered at any longitude or latitude because of
the symmetry of the spherical shell.

The spherical shell had dimensions of $r_1 = R$ ($R$ is the mean Earth radius) and $r_2 = R +
1\ km$ and density $\rho = 2.67\ g.cm^{-3}$.

The largest errors due are concentrated directly on top of the tesseroid
(Fig.~\ref{fig:sample}b).

Therefore, we perform the computations on an $11 \times 11$ point regular grid
in an area directly on top of the tesseroid with corner at $\lambda = 0^\circ$
$\phi = 0^\circ$.

The computation grid was located at a constant height above the spherical shell
$h = r_2 + 1\ km$.

Table~\ref{tab:shell} contains the parameters defining the spherical shell.

\begin{table}
    \caption{Parameters of the spherical shell.}
    \label{tab:shell}
    \begin{tabular}{lr}
        $\rho$                    & $2.76\ g.cm^{-3}$ \\
        $\Delta r$                & $1\ km$ \\
        $r_1 = R$                 & $6,378.137\ km$ \\
        $r_2 = r_1 + \Delta r$    & $6,379.137\ km$ \\
    \end{tabular}
\end{table}
